Manuscript title

### 2018-12-03 Manuscript/manuscript.Rmd
manuscript edits

Lastly, we evaluated models when using distance type predictors for the feature space. For the 5kb resolution data, tt was found that models with distance type predictors out performed models with count overlaps types across resolutions (Figure ).

This result was also observed when compared to models with percent overlap type predictors, regardless of the variable reduction technique used (Supplementary Table). The differences in performances was found to be most severe when looking at the F1-score and MCC (Supplementary Table).

Again referencing Figure 11, focusing on the rows corresponding to models using randomly under-sampled data, it was found that models with distance type predictors out performed models with the two other overlap types (counts and percents). The disparity between predictor types was steady across resolutions (Table 7). The greatest difference was seen in the 5kb data. For models with Elastic-Net regularization, the F1-scores were X, Y, and Z, while the MCCs were X, Y, and Z for each predictor type respectively.

###PERFORMANCES WORSEN AS RESOLUTION INCREASES

Figure 9 compares the results of random forest models using distance-type predictors, with elastic-net regularization, and random under-sampling, across each domain data resolution. We see that the results for F1-scores are relatively stable between 5kb, 25kb, and 50kb resolutions with a sharp decrease for the 100kb resolution. Furthermore, the decrease in performance is more evident and steady across accuracy, AUC, and MCC metrics.

###5kb RESOULTION DATA PROVIDES MOST ACCURATE ACCURATE RESULTS

To identify the functional genomic elements that were most predictive of TAD boundaries, we analyzed the variable importance produced by each random forest algorithm. Figure 10 presents the subsequent scaled importance plots of the top 15 most predictive genomic elements for each model presented in Figure 9. We see that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2. These results align with what is seen in the literature. Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature. The results from Figure 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.

>>>>

We then used the ensemble to compare models with distance type predictors for the feature space. For the 5kb resolution data, it was found that models with distance type predictors out performed models with either of the two overlap types (Figure 16). The improvement was observed across all 4 performance metrics that were considered (Supplementary Table 13). Likewise, improved performances were seen in the other 3 resolutions as well. Although overall performance decreased as resolution increased, models with distance type predictors still were able to maintain a profound improvement (Supplementary Figure 14;Supplementary Table 14).

###PERFORMANCES DEGRADE AS RESOLUTION INCREASES

Finally, we directly compared the performances of models across the different resolutions. The comparisons consisted of random forest models using distance type predictors, elastic-net regularization, and 50 iterations of random under-sampling. The model using 5kb resolution domain data was found to perform slightly better compared to the 25kb and 50kb resolutions (Figure 9). A sharp decrease in performance was seen in the 100kb resolution.

The differences in performances was most evident when analyzing the variable importance plots for each model using the 4 resolutions. We found that when we analyzed the variable importance produced by each random forest algorithm. We found that for the 5kb resolution, the most predictive elements include insulator proteins, DNase hypersensitive sites, the transcription factor CTCF, as well as histone modifications H3k9ac, H2az, and H3k4me2 (Figure 10 A). Although, the insulator protein is featured as a top predictor in 2 of the other 3 resolutions, the rest of the predictors are less consistent among each other and less in agreement with the literature (Figure 10 B-D). The results from Figures 9 and 10 confirm that the model results appear to degrade as resolution increases with respect to both prediction and the identification of genomic elements associated with TAD boundaries.
